Community Embeddings for Friend Suggestions

### 2020-10-12 paper-ffs.tex
use IEEEtranN
for more cite… support
https://tex.stackexchange.com/questions/201582/natbib-ieeetran-and-alphanumeric-citation-is-there-an-ieeetransan-style-availa
\citetitle -> \citet

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[super]{nth}

@@

The function $ComE(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ is the ComE BGMM+VI community embedding algorithm. It returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$. ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citetitle{ComE} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}. ComE BGMM+VI takes a Bayesian approach to community embedding by utilizing  a Bayesian Gaussian mixture model (BGMM) and variational inference (VI) for community embedding and detection instead of a non-Bayesian Gaussian mixture model (GMM) with expectation maximization (EM) \cite{ComE_BGMM_GH}. %TODO citation to the ComE BGMM paper.

@@

The small \citetitle{KarateClubDS} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.4\textwidth]{images/karateclub/spring.png}
    \caption{\citetitle{KarateClubDS} plotted with networkx's spring layout \cite{KarateClubDS, networkx}.}
    \label{fig:karateclub_spring}
\end{figure}

Fig. \ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \citetitle{KarateClubDS} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig. \ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.

@@

As can be seen in Fig. \ref{fig:karateclub_spring}, the two communities in the \citetitle{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$. Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset. The node classification obtained reflects the node classification published in the \citeyear{ComE} original ComE paper by \citeauthor{ComE}.\cite{ComE}

@@

\citetitle{KarateClubDS} is split into training and testing parts. For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\linewidth]{images/karateclub/embeddings_5.png}
    \caption{\citetitle{KarateClubDS} training dataset node and community embedding and node classification.}
    \label{fig:karateclub_emb}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=.4\textwidth]{images/karateclub/hit_rates.png}
    \caption{Hit-rates from top-$N$ recommendations on \citetitle{KarateClubDS}.}
    \label{fig:karateclub_hitrates}
\end{figure}

Fig. \ref{fig:karateclub_hitrates} shows promising results for using ComE to generate top-$N$ friend suggestions on the small \citetitle{KarateClubDS}. The achieved hit-rate starts at 33\% for $N=1$, reaches 67\% at $N=3$, and maxes out at 100\% for $N=7$; therefore, when presenting three friend suggestions to one test user, at least in $66\%$ of cases a friend suggestion would be of interest.

@@

The Social circles Facebook dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citetitle{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}

@@

%%% Bibliography
\bibliographystyle{IEEEtran}
\bibliography{literature}

>>>>

\usepackage{cite}
\usepackage[numbers]{natbib}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[super]{nth}

@@

The function $ComE(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ is the ComE BGMM+VI community embedding algorithm. It returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$. ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citet{ComE} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}. ComE BGMM+VI takes a Bayesian approach to community embedding by utilizing  a Bayesian Gaussian mixture model (BGMM) and variational inference (VI) for community embedding and detection instead of a non-Bayesian Gaussian mixture model (GMM) with expectation maximization (EM) \cite{ComE_BGMM_GH}. %TODO citation to the ComE BGMM paper.

@@

The small \citet{KarateClubDS} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.4\textwidth]{images/karateclub/spring.png}
    \caption{\citet{KarateClubDS} plotted with networkx's spring layout \cite{KarateClubDS, networkx}.}
    \label{fig:karateclub_spring}
\end{figure}

Fig. \ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \citet{KarateClubDS} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig. \ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.

@@

As can be seen in Fig. \ref{fig:karateclub_spring}, the two communities in the \citet{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$. Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset. The node classification obtained reflects the node classification published in the \citeyear{ComE} original ComE paper by \citeauthor{ComE}.\cite{ComE}

@@

\citet{KarateClubDS} is split into training and testing parts. For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\linewidth]{images/karateclub/embeddings_5.png}
    \caption{\citet{KarateClubDS} training dataset node and community embedding and node classification.}
    \label{fig:karateclub_emb}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=.4\textwidth]{images/karateclub/hit_rates.png}
    \caption{Hit-rates from top-$N$ recommendations on \citet{KarateClubDS}.}
    \label{fig:karateclub_hitrates}
\end{figure}

Fig. \ref{fig:karateclub_hitrates} shows promising results for using ComE to generate top-$N$ friend suggestions on the small \citet{KarateClubDS}. The achieved hit-rate starts at 33\% for $N=1$, reaches 67\% at $N=3$, and maxes out at 100\% for $N=7$; therefore, when presenting three friend suggestions to one test user, at least in $66\%$ of cases a friend suggestion would be of interest.

@@

The Social circles Facebook dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citet{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}

@@

%%% Bibliography
\bibliographystyle{IEEEtranN}
\bibliography{literature}
